Chemistry of fossil Pinus pollen and the effect of acetolysis

### 2020-12-10 manuscript.Rmd
wrote preproc and plotting function
wrote preprocess file and hook into manuscript

@@

# TODO

- extract fresh Pinus from images
- measure samples from 2 more cores (9 each)
- mark Alnus and BetCor on images
- extract Alnus BetCor from Dal samples
- extract fresh Alnus BetCor

>>>>

<!-- PRE-PROCESS DATA -->
```{r}
pre_process = TRUE
source(here("R","helper_functions.R"))
if (!hasName(DAL, "sg2")) {
  source(here("R","pre_process.R"))
} else {
  TSK = readRDS(here("data","output","TSK_spectra.rds"))
  MFM = readRDS(here("data","output","MFM_spectra.rds"))
  DAL = readRDS(here("data","output","DAL_spectra.rds"))
}
```

@@
